R Notebook

### 2023-12-01 02_paper/02_study/02_fitbit paper/analysis_171123.Rmd
fiiitbiiiiitttttttt

```{r}
library(needs)
needs(ltm,
      xtable,
      broom,
      ppcor,
      jtools,
      lm.beta,
      janitor,
      lubridate,
      readxl,
      ggthemes,
      gridExtra,
      imputeTS,
      DescTools,
      cowplot,
      rstatix,
      ggpubr,
      lme4,
      lmerTest,
      viridis,
      gridExtra,
      gridtext,
      magrittr,
      PerformanceAnalytics,
      Hmisc,
      corrplot,
      tidyverse,
      ggplot2,
      apaTables)

@@

main <- 
  main %>% 
  dplyr::select("time", "heart_rate", "ID", "time_span") %>% 
  distinct() %>% 
  group_by(ID) %>% 
  dplyr::summarize(mean_heart = mean(heart_rate),
            sd_heart = sd(heart_rate)) %>%
  ungroup() %>% 
  right_join(x = .,
             y = main,
             by = "ID") %>% 
  filter(!(time_span == "teaching" & time > 600)) %>%
  mutate(heart_rate_std = (heart_rate - mean_heart)/
           sd_heart)

@@

sd_mean <-
  fix_models %>%
  group_by(Phase) %>%
  dplyr::summarize(
    mean_slope = mean(slope),
    sd_slope = sd(slope),
    mean_intercept = mean(intercept),
    sd_intercept = sd(intercept)
  )

@@

```{r}
df_ttest <- 
  df_regression %>% 
  group_by(ID, time_span) %>% 
  summarize(mean_heart_rate = mean(heart_rate_std)) %>% 
  ungroup()
```

@@

```{r}
df_ttest_slope <- 
  fix_models %>% 
  group_by(id, Phase) %>% 
  summarize(mean_slope = mean(slope)) %>% 
  ungroup()
```

@@

# Multiple Linear Regression (Mean)
```{r}
main %>% 
  group_by(ID, time_span) %>% 
  summarize(disruption_factor = mean(disruption_factor,
                                     na.rm = T),
            confidence_factor = mean(confidence_factor,
                                     na.rm = T),
            teaching_experience = mean(teaching_experience),
            heart_rate = mean(heart_rate_std)
            ) %>% 
  ungroup() -> data_regression_mean

@@

# Multiple Linear Regression (Slope)
```{r}
df_multi <- 
  main %>% 
  select("ID",
         "disruption_factor",
         "confidence_factor",
         "teaching_experience") %>% 
  distinct() %>% 
  group_by(ID) %>% 
  summarize(disruption_factor = mean(disruption_factor, na.rm = T),
            confidence_factor = mean(confidence_factor, na.rm = T),
            teaching_experience) %>% 
  ungroup() %>% 
  mutate(id = as.character(ID),
         ) %>% 
  distinct() %>% 
  right_join(x = .,
            y = fix_models,
            by = "id") %>%
  mutate(time_span = factor(Phase,
                             levels = c("Pre Teaching Phase",
                                        "Teaching Phase",
                                        "Post Teaching Phase",
                                        "Interview Phase",
                                        "End Phase"),
                             labels = c("preparation",
                                        "teaching",
                                        "post",
                                        "interview",
                                        "end")
                            )
         ) %>%
  select("id",
         "disruption_factor",
         "confidence_factor",
         "teaching_experience",
         "slope",
         "time_span")

@@

summary(regr_post1)
summary(regr_post2)
summary(regr_post3)
summary(regr_post4)

summary(regr_end1)$r.squared - summary(regr_end2)$r.squared - summary(regr_end3)$r.squared - summary(regr_end4)$r.squared

@@

# left_join(x = df_heart_rate,
#           y = df_heart_rate_std,
#           by = c("ID","time")) %>% 
bind_rows(df_heart_rate,
          df_heart_rate_std
          ) %>% 
  ggplot(mapping = aes(x = time,
                       y = heart_rate
                       )
         ) +
  # geom_point(alpha = 0.05) + 
  geom_smooth(se = T,
              size = 0.5,
              colour = "black",
              level = 0.99) +
  scale_color_viridis_d(option = "A",
                        end = 0.8) +
  scale_linetype_manual(values = c(1, 6)) +
  # scale_x_continuous(expand = c(0, NA),
  #                    breaks = seq(0, 120, 10)) +
  scale_x_continuous(expand = c(0.01,0)) + 
  labs(x = "Time (in minutes)",
       #y = "Heart Rate (in Beats per Minute)",
       y = "",
       # title = "Figure #",
       # subtitle = "Overall Course of Average Heartrate",
#        caption = expression(paste(italic("Note: "),
# "The shadow around the line represents the 99% confidence interval. The confidence interval shown refers to the HR measurement points during the entire study period. We used the ggplot2 package (v3.3.3; Wickham, 2016) to calculate the moving average of the course."))
       ) +
  #ggtitle("Overall Course of Average Heartrate") +
  theme_apa() + 
  # theme(plot.subtitle = element_text(face = "italic"),
  #       plot.caption = element_text(hjust = 0),
  #       axis.line = element_line(colour = "black"),
  #       panel.grid.major = element_blank(),
  #       panel.grid.minor = element_blank(),
  #       panel.border = element_blank(),
  #       panel.background = element_blank()) +
  facet_wrap(~ type,
             ncol = 2,
             scales = "free_y")

@@

# Pre Teaching Phase
```{r echo = FALSE, results='asis'}
df_multi <- 
  main %>% 
  select("ID", "disruption_factor", "confidence_factor", "teaching_experience") %>% 
  distinct() %>% 
  group_by(ID) %>% 
  summarize(disruption_factor = mean(disruption_factor, na.rm = T),
            confidence_factor = mean(confidence_factor, na.rm = T),
            teaching_experience) %>% 
  ungroup() %>% 
  mutate(id = as.character(ID)) %>% 
  distinct() %>% 
  right_join(x = .,
            y = fix_models,
            by = "id")
  # mutate(posneg = if_else(condition = slope < 0,
  #                         true = "negative",
  #                         false = "positive"))

@@

```{r echo = FALSE, results='asis'}
df_multi <- 
  main %>% 
  select("ID", "disruption_factor", "confidence_factor", "teaching_experience") %>% 
  distinct() %>% 
  group_by(ID) %>% 
  summarize(disruption = mean(disruption_factor, na.rm = T),
            confidence = mean(confidence_factor, na.rm = T),
            teaching_experience) %>% 
  ungroup() %>% 
  mutate(id = as.character(ID)) %>% 
  distinct() %>% 
  right_join(x = .,
            y = fix_models,
            by = "id") %>% 
  # mutate(posneg = if_else(condition = slope < 0,
  #                         true = "negative",
  #                         false = "positive"))
fit_teach_1 <-
  df_multi %>% 
  filter(Phase == "Teaching Phase") %>% 
  # split(.$posneg) %>% 
  map(~ lm(slope ~ disruption,
           data = .))

@@

```{r echo = FALSE, results='asis'}
df_multi <- 
  main %>% 
  select("ID", "disruption_factor", "confidence_factor", "teaching_experience") %>% 
  distinct() %>% 
  group_by(ID) %>% 
  summarize(disruption = mean(disruption_factor, na.rm = T),
            confidence = mean(confidence_factor, na.rm = T),
            teaching_experience) %>% 
  ungroup() %>% 
  mutate(id = as.character(ID)) %>% 
  distinct() %>% 
  right_join(x = .,
            y = fix_models,
            by = "id") %>% 
  mutate(posneg = if_else(condition = slope < 0,
                          true = "negative",
                          false = "positive"))

>>>>

```{r}
library(needs)
needs(ltm,
      xtable,
      broom,
      ppcor,
      jtools,
      lm.beta,
      janitor,
      lubridate,
      readxl,
      ggthemes,
      gridExtra,
      imputeTS,
      DescTools,
      cowplot,
      rstatix,
      ggpubr,
      lme4,
      lmerTest,
      viridis,
      gridExtra,
      gridtext,
      magrittr,
      PerformanceAnalytics,
      Hmisc,
      corrplot,
      tidyverse,
      ggplot2)

@@

main <- 
  main %>% 
  dplyr::select("time", "heart_rate", "ID", "time_span") %>% 
  distinct() %>% 
  group_by(ID) %>% 
  dplyr::summarise(mean_heart = mean(heart_rate),
            sd_heart = sd(heart_rate)) %>%
  ungroup() %>% 
  right_join(x = .,
             y = main,
             by = "ID") %>% 
  filter(!(time_span == "teaching" & time > 600)) %>%
  mutate(heart_rate_std = (heart_rate - mean_heart)/
           sd_heart)

@@

sd_mean <-
  fix_models %>%
  group_by(Phase) %>%
  dplyr::summarise(
    mean_slope = mean(slope),
    sd_slope = sd(slope),
    mean_intercept = mean(intercept),
    sd_intercept = sd(intercept)
  )

@@

```{r}
df_ttest <- 
  df_regression %>% 
  group_by(ID, time_span) %>% 
  summarise(mean_heart_rate = mean(heart_rate_std)) %>% 
  ungroup()
```

@@

```{r}
df_ttest_slope <- 
  fix_models %>% 
  group_by(id, Phase) %>% 
  summarise(mean_slope = mean(slope)) %>% 
  ungroup()
```

@@

# Multiple Linear Regression (Mean)
```{r}
main %>% 
  group_by(ID, time_span) %>% 
  summarise(disruption_factor = mean(disruption_factor,
                                     na.rm = T),
            confidence_factor = mean(confidence_factor,
                                     na.rm = T),
            teaching_experience = mean(teaching_experience),
            heart_rate = mean(heart_rate_std)
            ) %>% 
  ungroup() -> data_regression_mean

@@

# Multiple Linear Regression (Slope)
```{r}
df_multi <- 
  main %>% 
  dplyr::select("ID",
         "disruption_factor",
         "confidence_factor",
         "teaching_experience") %>% 
  distinct() %>% 
  group_by(ID) %>% 
  summarise(disruption_factor = mean(disruption_factor, na.rm = T),
            confidence_factor = mean(confidence_factor, na.rm = T),
            teaching_experience) %>% 
  ungroup() %>% 
  mutate(id = as.character(ID),
         ) %>% 
  distinct() %>% 
  right_join(x = .,
            y = fix_models,
            by = "id") %>%
  mutate(time_span = factor(Phase,
                             levels = c("Pre Teaching Phase",
                                        "Teaching Phase",
                                        "Post Teaching Phase",
                                        "Interview Phase",
                                        "End Phase"),
                             labels = c("preparation",
                                        "teaching",
                                        "post",
                                        "interview",
                                        "end")
                            )
         ) %>%
  dplyr::select("id",
         "disruption_factor",
         "confidence_factor",
         "teaching_experience",
         "slope",
         "time_span")

@@

summary(regr_interview1)
summary(regr_interview2)
summary(regr_interview3)
summary(regr_interview4)

summary(regr_teaching2)$r.squared - summary(regr_teaching1)$r.squared

- summary(regr_end3)$r.squared - summary(regr_end4)$r.squared

@@

# left_join(x = df_heart_rate,
#           y = df_heart_rate_std,
#           by = c("ID","time")) %>% 
bind_rows(df_heart_rate,
          df_heart_rate_std
          ) %>% 
  ggplot(mapping = aes(x = time,
                       y = heart_rate
                       )
         ) +
  # geom_point(alpha = 0.05) + 
  geom_smooth(se = T,
              size = 0.5,
              colour = "black",
              level = 0.99) +
  scale_color_viridis_d(option = "A",
                        end = 0.8) +
  scale_linetype_manual(values = c(1, 6)) +
  # scale_x_continuous(expand = c(0, NA),
  #                    breaks = seq(0, 120, 10)) +
  scale_x_continuous(expand = c(0.01,0)) + 
  labs(x = "Time (in Minutes)",
       #y = "Heart Rate (in Beats per Minute)",
       y = "",
       # title = "Figure #",
       # subtitle = "Overall Course of Average Heartrate",
#        caption = expression(paste(italic("Note: "),
# "The shadow around the line represents the 99% confidence interval. The confidence interval shown refers to the HR measurement points during the entire study period. We used the ggplot2 package (v3.3.3; Wickham, 2016) to calculate the moving average of the course."))
       ) +
  #ggtitle("Overall Course of Average Heartrate") +
  theme_apa() + 
  # theme(plot.subtitle = element_text(face = "italic"),
  #       plot.caption = element_text(hjust = 0),
  #       axis.line = element_line(colour = "black"),
  #       panel.grid.major = element_blank(),
  #       panel.grid.minor = element_blank(),
  #       panel.border = element_blank(),
  #       panel.background = element_blank()) +
  facet_wrap(~ type,
             ncol = 2,
             scales = "free_y")

@@

# Pre Teaching Phase
```{r echo = FALSE, results='asis'}
df_multi <- 
  main %>% 
  select("ID", "disruption_factor", "confidence_factor", "teaching_experience") %>% 
  distinct() %>% 
  group_by(ID) %>% 
  summarise(disruption_factor = mean(disruption_factor, na.rm = T),
            confidence_factor = mean(confidence_factor, na.rm = T),
            teaching_experience) %>% 
  ungroup() %>% 
  mutate(id = as.character(ID)) %>% 
  distinct() %>% 
  right_join(x = .,
            y = fix_models,
            by = "id")
  # mutate(posneg = if_else(condition = slope < 0,
  #                         true = "negative",
  #                         false = "positive"))

@@

```{r echo = FALSE, results='asis'}
df_multi <- 
  main %>% 
  select("ID", "disruption_factor", "confidence_factor", "teaching_experience") %>% 
  distinct() %>% 
  group_by(ID) %>% 
  summarise(disruption = mean(disruption_factor, na.rm = T),
            confidence = mean(confidence_factor, na.rm = T),
            teaching_experience) %>% 
  ungroup() %>% 
  mutate(id = as.character(ID)) %>% 
  distinct() %>% 
  right_join(x = .,
            y = fix_models,
            by = "id") %>% 
  # mutate(posneg = if_else(condition = slope < 0,
  #                         true = "negative",
  #                         false = "positive"))
fit_teach_1 <-
  df_multi %>% 
  filter(Phase == "Teaching Phase") %>% 
  # split(.$posneg) %>% 
  map(~ lm(slope ~ disruption,
           data = .))

@@

```{r echo = FALSE, results='asis'}
df_multi <- 
  main %>% 
  select("ID", "disruption_factor", "confidence_factor", "teaching_experience") %>% 
  distinct() %>% 
  group_by(ID) %>% 
  summarise(disruption = mean(disruption_factor, na.rm = T),
            confidence = mean(confidence_factor, na.rm = T),
            teaching_experience) %>% 
  ungroup() %>% 
  mutate(id = as.character(ID)) %>% 
  distinct() %>% 
  right_join(x = .,
            y = fix_models,
            by = "id") %>% 
  mutate(posneg = if_else(condition = slope < 0,
                          true = "negative",
                          false = "positive"))

### 2023-12-01 02_paper/02_study/02_fitbit paper/analysis_270423.Rmd
fiiitbiiiiitttttttt

```{r}
library(needs)
needs(ltm,
      xtable,
      broom,
      ppcor,
      jtools,
      lm.beta,
      janitor,
      lubridate,
      readxl,
      ggthemes,
      gridExtra,
      imputeTS,
      DescTools,
      cowplot,
      rstatix,
      ggpubr,
      lme4,
      lmerTest,
      viridis,
      gridExtra,
      gridtext,
      magrittr,
      PerformanceAnalytics,
      Hmisc,
      corrplot,
      tidyverse,
      ggplot2,
      apaTables,
      rockchalk)

@@

  main %>% 
  select("ID", "disruption_factor", "confidence_factor", "teaching_experience") %>% 
  distinct() %>% 
  group_by(ID) %>% 
  # summarize(disruption_factor = mean(disruption_factor, na.rm = T),
  #           confidence_factor = mean(confidence_factor, na.rm = T),
  #           teaching_experience) %>% 
  transmute(id = as.character(ID),
            disruption_factor = mean(disruption_factor, na.rm = T),
            confidence_factor = mean(confidence_factor, na.rm = T),
            teaching_experience) %>% 
  ungroup() %>% 
  distinct() %>% 
  right_join(x = .,
            y = fix_models,
            by = "id") -> data_regression_slope

>>>>

```{r}
library(needs)
needs(ltm,
      xtable,
      broom,
      ppcor,
      jtools,
      lm.beta,
      janitor,
      lubridate,
      readxl,
      ggthemes,
      gridExtra,
      imputeTS,
      DescTools,
      cowplot,
      rstatix,
      ggpubr,
      lme4,
      lmerTest,
      viridis,
      gridExtra,
      gridtext,
      magrittr,
      PerformanceAnalytics,
      Hmisc,
      corrplot,
      tidyverse,
      ggplot2)

@@

main %>% 
  dplyr::select("ID", "disruption_factor", "confidence_factor", "teaching_experience") %>% 
  distinct() %>% 
  group_by(ID) %>% 
  # summarise(disruption_factor = mean(disruption_factor, na.rm = T),
  #           confidence_factor = mean(confidence_factor, na.rm = T),
  #           teaching_experience) %>% 
  transmute(id = as.character(ID),
            disruption_factor = mean(disruption_factor, na.rm = T),
            confidence_factor = mean(confidence_factor, na.rm = T),
            teaching_experience) %>% 
  ungroup() %>% 
  distinct() %>% 
  right_join(x = .,
            y = fix_models,
            by = "id") -> data_regression_slope
